% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \documentclass[a4paper,10pt,oneside]{article}
%\documentclass[letterpaper,10pt,oneside]{article}
% change font size
\documentclass[letterpaper,10pt,oneside]{article}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TYPESETTING OPTIONS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\TypesetInNonStopMode}{1}
\newcommand{\TypesetInDraftMode}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVAuthor}{Yifei Liu}
\newcommand{\CVTitle}{Yifei Liu Curriculum Vitae}
\newcommand{\CVNote}{CV updated on {\DatestampYM{2021}{05}} }
\newcommand{\CVWebpage}{\homepage{http://www.fsl.cs.stonybrook.edu/\textasciitilde yifei/}}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
%\href{https://www.google.com/maps/place/New+Computer+Science+Stony+Brook+University,+Stony Brook}
{Room 336, New CS Building, Stony Brook, NY 11794-2424}
\,\BulletSymbol\,
Cell: +1 631-710-8377
\par
\href{mailto:yifeliu@cs.stonybrook.edu}
{yifeliu@cs.stonybrook.edu}
\,\BulletSymbol\,
\href{\CVWebpage}
{\CVWebpage}
\,\BulletSymbol\,
\href{https://www.linkedin.com/in/yifei-liu/}
{linkedin.com/in/yifei-liu/}
\newline
Visa: F-1 Student
\,\BulletSymbol\,
Timezone: US/Eastern
\end{subtitle}

\begin{body}
%%%%%%%%%%%%%%%%%%%%%%%%
%% Research Interests %%
%%%%%%%%%%%%%%%%%%%%%%%%
\section
{Research Interests}
{Research Interests}
{PDF:ResearchInterests}
File/Storage Systems, Operating Systems, and Machine Learning for Systems.


\BigGap

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}
%\href{https://www.stonybrook.edu/}
{\textbf{Stony Brook University}}
\hfill
Stony Brook, NY

\GapNoBreak
\BulletItem
Ph.D. in
%\href{https://www.cs.stonybrook.edu/}
{Computer Science}
\hfill
08/2019 -- Present
\begin{detail}
\BulletItem
CGPA: 3.91 / 4.0 
\BulletItem
\emph{Courses}: CSE505 Computing with Logic; CSE506 Operating Systems; 
CSE512  Machine Learning; CSE532 Theory of Database Systems; CSE544 
Probability and Statistics for Data Science; CSE548 Analysis of Algorithms

\end{detail}

\BigGap

%\href{http://english.hust.edu.cn/}
{\textbf{Huazhong University of Science and Technology}}
\hfill
Wuhan, China

\GapNoBreak
\BulletItem
M.Sc. in
%\href{http://english.wnlo.hust.edu.cn/}
{Computer System Architecture}
\hfill
09/2016 -- 06/2019
\begin{detail}
\BulletItem
CGPA: 85.02 / 100 
%\SubBulletItem
%\emph{Relevant Courses}: Parallel Processing; Theory and Technology of Information Storage; Advanced Computer Architecture; Theory of matrices; Data Mining and Retrieval; Pattern Recognition. 
\BulletItem
\emph{Thesis}: Research on Metadata Organization Approach for Image Storage Systems towards Content-based Semantic Similarity Query
\end{detail}

\BigGap
%\href{http://www.hzau.edu.cn/en/HOME.htm}
{\textbf{Huazhong Agricultural University}}
\hfill
Wuhan, China
\GapNoBreak
\BulletItem
B.Eng. in
%\href{http://coi.hzau.edu.cn/}
{Computer Science and Technology}
\hfill
09/2012 -- 06/2016
\begin{detail}

\BulletItem
CGPA: 3.43 / 4.00 \quad Major GPA: 3.79 / 4.00 \quad Rank: 9/118
%\SubBulletItem
%\emph{Relevant Courses}: Data Structure; Operating System; Principles of Computer Composition; Computer Networks; Compilers Principles; Algorithm Analysis and Design; Programming and Application of Linux.
\BulletItem
\emph{Thesis}: Predicting Disk Failures based on Machine Learning Methods
\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Experience}
{Experience}
{PDF:Experience}
%\href{https://www.fsl.cs.stonybrook.edu/}
{\textbf{File systems and Storage Lab (FSL), Stony Brook University}}
\hfill
Stony Brook, NY

\emph{Graduate Research Assistant}
\hfill
05/2020 --
Present
\GapNoBreak
Advisor: Prof. Erez Zadok
\BulletItem
Design and benchmark multi-tier caching systems with intelligent MRC analysis. 
\BulletItem
Apply model checking to verify file systems formally and automatically.

\BigGap
%\href{https://www.stonybrook.edu/}
{\textbf{Stony Brook University}}
\hfill
Stony Brook, NY

\emph{Graduate Teaching Assistant}
\hfill
08/2019 --
05/2020
\GapNoBreak
\BulletItem
CSE376 Advanced Systems Programming in Unix/C (S' 21, S'20). Instructor: Prof. Erez Zadok
\BulletItem
CSE306 Operating Systems (F'19). Instructor: Prof. Eugene Stark


\BigGap
%\href{http://english.wnlo.hust.edu.cn/}
{\textbf{Wuhan National Laboratory for Optoelectronics}}
\hfill
Wuhan, China

\emph{Master's Student/Research Assistant}
\hfill
09/2016 --
06/2019
\GapNoBreak
Advisor: Prof. Ke Zhou

\GapNoBreak
\BulletItem
Used deep learning hash to design and implement a metadata system for integration of high-precision and low-latency content-based semantic queries in storage systems

\GapNoBreak
\BulletItem
Proposed a framework for assessing image ``dark data'' based on a novel semantic hash ranking (SHR) algorithm

\GapNoBreak
\BulletItem
Performed theoretical analysis on hash-based graphs to facilitate rank algorithms and graph database operations

%\begin{detail}
%\SubBulletItem
%Project:
%Investigations on the Use of Lasers to Measure Climate Change
%\SubBulletItem
%Supervisors:
%Professor Jane Citizen and
%Dr Ann Yone
%\SubBulletItem
%Research areas:
%Climate change, lasers, statistical analysis, data analytics.
%\end{detail}

%Tencent
\BigGap
%\href{https://www.tencent.com/en-us/index.html}
{\textbf{Tencent}} %(\#1 social media, Internet corporation in Asia)
\hfill
Shenzhen, China

\emph{Backend Developer Intern}
\hfill
12/2015 --
08/2016
\GapNoBreak
\BulletItem
Predicted disk failures with disk data collected via machine learning algorithms to achieve high precision and recall

\GapNoBreak
\BulletItem
Built infrastructure for collecting long-term disk S.M.R.A.T. data from over 10,000 servers in Tencent data centers

\GapNoBreak
\BulletItem
Tested cache replacement policies on Tencent application traces

%ICT,CAS
\BigGap
%\href{http://english.ict.cas.cn/}
{\textbf{Institute of Computing Technology, Chinese Academy of Sciences}}
\hfill
Beijing, China

\emph{Intern/Visiting Student}
\hfill
11/2015 --
12/2015
\GapNoBreak
\BulletItem
Explored the correlation between Apache Spark and JVM GC parameters

%Chinasoft International
%\BigGap
%\href{http://www.chinasofti.com/en/index.shtml}
%{\textbf{Chinasoft International Ltd}}
%\hfill
%Guangzhou, China

%\emph{Front-end Student Intern}
%\hfill
%07/2015 --
%08/2015
%\GapNoBreak
%\BulletItem
%Collaborated with other interns to develop a catering website using jQuery, AJAX, Java Servlet

%Huazhong Agricultural University
\BigGap
%\href{http://www.hzau.edu.cn/en/HOME.htm}
{\textbf{Huazhong Agricultural University}}
\hfill
Wuhan, China

\emph{Undergraduate Research Assistant}
\hfill
11/2014 --
06/2015
\GapNoBreak
Supervisors: Prof. Jianxiao Liu and Prof. Ruifang Zhai
\GapNoBreak
\BulletItem
Used Bayesian Network Reasoning to propose a web service recommendation approach for organizing and recommending a set of correlated services

\GapNoBreak
\BulletItem
Designed an image line detection algorithm for automatically measuring character parameters of the rapeseed plant

\GapNoBreak
\BulletItem
Developed a GUI for counting the number of cotton cells in microscopic images (for the Huazhong Agricultural University's College of Plant Science \& Technology)


%%%%%%%%%%%%%%%%%%%%%
%% TEACHING %%
%%%%%%%%%%%%%%%%%%%%%
%\section
%{Teaching}
%{Teaching}
%{PDF:Teaching}
%\textbf{Graduate Teaching Assistant, Stony Brook University}
%\hfill
%08/2019 --
%05/2020

%\GapNoBreak
%\BulletItem
%CSE376 Advanced Systems Programming in Unix/C (S'21, S'20). Professor: Erez Zadok

%\GapNoBreak
%\BulletItem
%CSE306 Operating Systems (F'19). Professor: Eugene Stark


%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\section
{Publications}
{Publications}
{PDF:Publications}

\iffalse
\subsection
{Journals}
{Journals}
{PDF:Journals}

\GapNoBreak
\NumberedItem{[11]}
%\href{http://www.example.com/my-paper-doi-5}
{\underline{J.~Doe}, J.~Citizen, and A.~Yone,
``On lasers and climate change,''
\textit{Journal of Science},
vol.~89,
no.~2,
pp.~4123--4133,
\DatestampYM{2008}{02}.}

% Note the use of {\CharSpace} for aligning shorter numbers.
\Gap
\NumberedItem{{\CharSpace}[1]}
%\href{http://www.example.com/my-paper-doi-4}
{\underline{J.~Doe} and J.~Citizen,
``Measuring the extent of climate change,''
\textit{Global Scientific Journal},
vol.~12,
no.~4,
pp.~330--352,
\DatestampYM{2006}{12}.}
\fi

%\BigGap
%\subsection
%{Conferences}
%{Conferences}
%{PDF:Conferences}

%\GapNoBreak
%SwiftGraph Paper
%\NumberedItem{[5]}
%\underline{J.~Doe}, J.~Citizen, and A.~Yone,
%``On lasers and climate change,''
%in \textit{Proceedings of the Laser Symposium},
%Las Vegas, Nevada, USA,
%\DatestampYM{2007}{01}.
\subsection
{Journal Articles}
{Journal Articles}
{PDF:JournalArticles}
\GapNoBreak

\NumberedItem{[1]}
Ke Zhou, Yangtao Wang, Yu Liu, Yujuan Yang, \underline{Yifei Liu}, Guoliang Li, Lianli Gao, and Zhili Xiao.
``A Framework for Image Dark Data Assessment.'' 
\textit{World Wide Web},
\DatestampY{2020}.

\BigGap
\NumberedItem{[2]}
%\href{https://www.sciencedirect.com/science/article/pii/S0167739X19302304}
Yu Liu, Yangtao Wang, Ke Zhou, Yujuan Yang, and \underline{Yifei Liu}.
``Semantic-aware Data Quality Assessment for Image Big Data.'' 
\textit{Future Generation Computer Systems (FGCS)},
\DatestampY{2020}.
\BigGap
\GapNoBreak

\subsection
{Conference Papers}
{Conference Papers}
{PDF:ConferencePapers}
\GapNoBreak
\NumberedItem{[1]}
Wei Su, \underline{Yifei Liu}, Gomathi Ganesan, Gerard Holzmann, Geoff Kuenning, Scott Smolka, and Erez Zadok.
``Model-Checking Support for File System Development.'' (Under Review)

\BigGap
\NumberedItem{[2]}
Yu Liu, Hong Jiang, Yangtao Wang, Ke Zhou, \underline{Yifei Liu}, and Li Liu.
``Content Sifting Storage: Achieving Fast Read for Large-scale Image Dataset Analysis.''
In \textit{Proceedings of the 57th Design Automation Conference (DAC)}, San Francisco, CA,
\DatestampY{2020}.

%Graph Analysis Paper
\BigGap
\NumberedItem{[3]}
%\href{https://link.springer.com/chapter/10.1007/978-3-030-26072-9_22}
Yangtao Wang, Yu Liu, \underline{Yifei Liu}, Ke Zhou, Yujuan Yang, Jiangfeng Zeng, Xiaodong Xu, and Zhili Xiao.
``Analysis and Management to Hash-Based Graph and Rank.''
In \textit{Proceedings of the 3rd APWeb-WAIM joint conference on Web and Big Data (APWeb-WAIM)}, Chengdu, China,
\DatestampY{2019}.

%dark data paper
\BigGap
\NumberedItem{[4]}
%\href{https://link.springer.com/chapter/10.1007/978-3-030-26072-9_1}
Yu Liu, Yangtao Wang, Ke Zhou, Yujuan Yang, \underline{Yifei Liu}, Jingkuan Song, and Zhili Xiao.
``A Framework for Image Dark Data Assessment.''
In \textit{Proceedings of the 3rd APWeb-WAIM joint conference on Web and Big Data (APWeb-WAIM)}, Chengdu, China,
\DatestampY{2019}.

%SCC 2018
\BigGap
\NumberedItem{[5]}
%\href{https://link.springer.com/chapter/10.1007/978-3-319-94376-3_2}
{Jianxiao Liu, Zonglin Tian, \underline{Yifei Liu}, and Liang Zhao.
``Research of Web Service Recommendation Using Bayesian Network Reasoning.''
In \textit{Proceedings of the 15th International Conference on Services Computing (SCC)},
Seattle, WA,
\DatestampY{2018}.}

% Note the use of {\CharSpace} for aligning shorter numbers.
%Agro-Geoinformatics
\BigGap
\NumberedItem{[6]}
%\href{https://ieeexplore.ieee.org/abstract/document/7248122/}
{Pujuan Shi, \underline{Yifei Liu}, Yihang Fang, Chengda Lin, and Ruifang Zhai.
``A new line detection algorithm - Automatic measurement of character parameter of rapeseed plant by LSD.''
In \textit{Proceedings of the 4th International Conference on Agro-Geoinformatics (Agro-Geoinformatics)},
Istanbul, Turkey,
\DatestampY{2015}.}
\BigGap
\GapNoBreak

\subsection
{Patents}
{Patents}
{PDF:Patents}
\GapNoBreak

\NumberedItem{[1]}
%\href{https://patents.google.com/patent/CN110413807B}
Ke Zhou, \underline{Yifei Liu}, Yu Liu, Yangtao Wang, and Yujuan Yang. A kind of image inquiry method and system based on contents semantic metadata. Chinese patent No. CN110413807B, Filed June, 2019. Granted April, 2021.

%Graph Analysis Paper
\BigGap
\NumberedItem{[2]}
%\href{https://patents.google.com/patent/CN110390352A}
Ke Zhou, Yu Liu, Yujuan Yang, Hua Wang, Chunhua Li, Yangtao Wang, and \underline{Yifei Liu}. A kind of dark data value appraisal procedure of image based on similitude Hash. CN110390352A, June 2019. (Under substantive examination)

%%%%%%%%%%%%%%%%%%%%%
%% PRESENTATIONS %%
%%%%%%%%%%%%%%%%%%%%%
\section
{Talks}
{Talks}
{PDF:Talks}
\BulletItem
\emph{OS Support for File System Model Checking}, 
Computer Science Graduate Research Day 2021, Stony Brook, NY.
\GapNoBreak


%%%%%%%%%%%%%%%%%%%%%
%% ACADEMIC AWARDS %%
%%%%%%%%%%%%%%%%%%%%%

\section
{Contest Awards}
{Contest Awards}
{PDF:ContestAwards}

%\BulletItem
%Second Prize, National Postgraduate Mathematic Contest in Modeling, China, 2016.
%\begin{detail}
%\SubBulletItem
%Winning rate 
%(\textbf{1732/8894 \textasciitilde19.47\%})
%\end{detail}
%\GapNoBreak

\BulletItem
Finalist, Interdisciplinary Contest in Modeling (MCM/ICM), USA, 2015.
\begin{detail}
\SubBulletItem
One of 52 winning teams in the world. First awardee of my university. (Rate: \textbf{52/9773 \textasciitilde0.53\%})
\end{detail}

\Gap
\BulletItem
National First Prize, National Postgraduate Mathematic Contest in Modeling, China, 2014.
\begin{detail}
\SubBulletItem
Won the highest award of this contest. 
(Rate: \textbf{120/4900 \textasciitilde2.4\%}) 
\end{detail}

\Gap
\BulletItem
National First Prize, Contemporary Undergraduate Mathematical Contest in Modeling, China, 2014.
\begin{detail}
\SubBulletItem
Won the highest award of this contest.
(Rate: \textbf{293/22233 \textasciitilde1.3\%})
\end{detail}

%%%%%%%%%%%%%%%%%%
%% OTHER AWARDS %%
%%%%%%%%%%%%%%%%%%

\section
{Academic Awards}
{Academic Awards}
{PDF:AcademicAwards}

\subsection
{Huazhong University of Science and Technology}
{Huazhong University of Science and Technology}
{PDF:HUST}
\GapNoBreak

\BulletItem
APWeb-WAIM Best Paper Runner-Up
\hfill
\DatestampY{2019}

\GapNoBreak

\BulletItem
Outstanding Graduate
\hfill
Spring \DatestampY{2019}

\GapNoBreak

\BulletItem
Merit Graduate Student (2 times)
\hfill
\DatestampY{2017} --
\DatestampY{2019}

\GapNoBreak
\BulletItem
First-class Academic Scholarship (3 times)
\hfill
\DatestampY{2016} --
\DatestampY{2019}
\BigGap
\GapNoBreak
\subsection
{Huazhong Agricultural University}
{Huazhong Agricultural University}
{PDF:HZAU}

\BulletItem
Outstanding Graduate
\hfill
Spring \DatestampY{2016}

\GapNoBreak
\BulletItem
BioMarker Scholarship 
\hfill
Fall \DatestampY{2015}

\GapNoBreak
\BulletItem
First Prize for Excellent Study 
 %(\textasciitilde 4/118)
\hfill
Spring \DatestampY{2015}

\GapNoBreak
\BulletItem
Merit Undergraduate Student (2 times)
\hfill
\DatestampY{2014} --
\DatestampY{2016}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%
\iffalse
\section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
English: Native language.

\GapNoBreak
\BulletItem
Spanish: Fluent (speaking, reading, writing).

\GapNoBreak
\BulletItem
Latin: Intermediate (reading); basic (speaking, writing).
\fi
%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}

%\subsection
%{Technical Skills}
%{Technical Skills}
%{PDF:TechnicalSkills}
%\GapNoBreak

\subsection
{Programming Languages}
{Programming Languages}
{PDF:ProgrammingLanguages}
\GapNoBreak
\BulletItem
Familiar ($\geq$ 4 years of experience): C, C++, Python

\GapNoBreak
\BulletItem
Intermediate (1 {\textasciitilde} 3 years): MATLAB, Bash, SQL, Java, Cypher

\GapNoBreak
\BulletItem
Basic ($\leq$ 1 year): JavaScript, Prolog
\BigGap
\GapNoBreak
\subsection
{Technologies}
{Technologies}
{PDF:Technologies}

\GapNoBreak
\BulletItem
\textbf{Databases:} MySQL (3 years), Neo4j (2 years), DB2 ($<$ 1 year), HBase ($<$ 1 year)

\GapNoBreak
\BulletItem
\textbf{File and Storage:} Linux VFS (2 years), OpenStack Swift (2 years), HDFS ($<$ 1 year)


%\GapNoBreak
%\BulletItem
%Deep learning platforms: Caffe, TensorFlow

\GapNoBreak
\BulletItem
\textbf{Operating Systems:} Linux (6 years), Windows 10 (4 years), MacOS (2 years), Linux kernel development (1 year)


\GapNoBreak
\BulletItem
\textbf{Parallel Computing:} Hadoop (1 year), Spark ($<$ 1 year)

\GapNoBreak
\BulletItem
\textbf{Tools:} VSCode (5 years), Git (3 years), Vim (3 years), Makefile (3 years), {\LaTeX} (3 years), GDB (2 years), Elasticsearch (1 year), CMake (1 year), Scikit-learn (1 year)

\BigGap
\subsection
{Human Languages}
{Human Languages}
{PDF:HumanLanguages}
\GapNoBreak
\BulletItem
Chinese (Native), English (Fluent)

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\section
{Certifications}
{Certifications}
{PDF:Certifications}
Machine Learning - Stanford Univeristy (2016), Coursera
\GapNoBreak

%%%%%%%%%%%%%%%
%% TestScore %%
%%%%%%%%%%%%%%%

%\section
%{Test Score}
%{Test Score}
%{PDF:TestScore}
%\textbf{GRE}: 
%Total 323 + 3.5 (Verbal 157 + Quantitative 166 + Analytical Writing %3.5)

%\GapNoBreak

%\BigGap
%\textbf{TOEFL}:
%Total 94 (Reading 28 + Listening 24 + Speaking 20 + Writing 22)

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%
\iffalse
\section
{References}
{References}
{PDF:References}

\BulletItem
\textbf{Ke Zhou}
\newline
Professor
\newline
School of Computer Science and Technology
\newline
Huazhong University of Science and Technology
\begin{detail}
\SubBulletItem
%1000 First Avenue, Springfield, Massachusetts 22222, USA
%\newline
%\href{k.zhou@hust.edu.cn}
{k.zhou@hust.edu.cn}
\,\SubBulletSymbol\,
+86\,139-7107-5916
\end{detail}
\fi

\end{body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\begin{flushright}
\UseNoteFont%
[\textit{\CVNote}]%
\hspace{2.0mm}\null
\end{flushright}

\label{LastPage}~
\end{document}
